\plaintitle

### 2016-12-13 drafts/labor/relationships.tex
piecework literature review section mostly updated. the various research questions might still be a bit of a mess

\subsubsection{\crowdworkpers}
\begin{comment}
	- Workers do it for money
	- Workers coordinate and communicate (gray, being a turker, team stuff). there is mega-drama
	- Workers don't like requesters. have tried to organize
\end{comment}

@@

% \topic{The relationships of workers
% % with their work,
% with their peers and
% with requesters
% are nuanced and not especially well--understood.}
% We can break this general body of work into two subgroups:
% workers' relationships
% \begin{inlinelist}
% % \item with \textit{work}, % \nameref{ch:workRelationship},
% \item with \textit{requesters}, and
% \item with \textit{other workers}.
% \end{inlinelist}
% We'll look at workers' relationships with work itself, which we'll discover
% gives us insight into why people engage in crowd work in the first place.

Workers' relationships with requesters are fraught.
% \topic{\ali{some topic sentence that brings together the debate where
% one side blames Turkers for being bad at Turking and
% another side blames requesters for not understanding Turkers as a culture of people.}}
Workers are often blamed for any low-quality work, regardless of whether they are responsible~\cite{martin2014being,takingAHITMcInnis}.
Some research is extremely open about this position, blaming unpredictable work on ``malicious'' workers~\cite{MaliciousCrowdworkersGadiraju} or those with ``a lack of expertise, dedication [or] interest''~\cite{Sheng:2008:GLI:1401890.1401965}.
% (see, for example, \citeauthor{MaliciousCrowdworkersGadiraju}'s work,
% which frames the problem of unpredictable work as the result of ``malicious'' crowd workers),
% \cite{MaliciousCrowdworkersGadiraju,Sheng:2008:GLI:1401890.1401965,Ipeirotis:2010:QMA:1837885.1837906}.
Workers resent this position --- for good reason.
\citeauthor{turkopticon} highlighted the information asymmetry between workers and requesters on AMT, leading to the creation of \TO, a site which allows Turkers to rate and review requesters~\cite{turkopticon}.
Dynamo then took this critique on information asymmetry and power imbalances a step further, designing a platform to facilitate
Turkers acting collectively to bring about changes to their circumstances~\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters~\cite{fixingChaos,dynamo}.

@@

% \topic{The frustration that workers experience dealing with requesters
% seems to precipitate frustration and mistrust between crowd workers, as well.}
% \citeauthor{dynamo} describes ``mega--drama'' among workers on forums for Turkers;
% \citeauthor{irani2015cultural} and \citeauthor{storiesIraniSilberman} discuss
% the culture of crowd work and the study thereof.
% \citeauthor{crowdcollab} quantifies and maps this social network of Turkers.
% \citeauthor{takingAHITMcInnis} takes these observations and considers
% what a crowd work platform might look like if it were to be designed more inclusively
% \cite{dynamo,irani2015cultural,storiesIraniSilberman,crowdcollab,takingAHITMcInnis}.
% The overarching theme of the research in this space has been
% documenting the struggle of crowd workers
% and attempting to intervene in constructive ways, while walking the balancing act
% (especially in the cases of \citeauthor{irani2015cultural} and later \citeauthor{storiesIraniSilberman})
% as we think about the culture of crowd workers.

\subsubsection{\pieceworkpers}
Early observers believed that workers were strongly motivated by the piecework model.
\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand.''
Workers' situations were quite dire: \citeauthor{riisOtherSideLives}  documented abhorrent working and living conditions of pieceworkers in New York City~\cite{riisOtherSideLives}.

% Workers' relationships with employers quickly soured.
% The match--girls strike of 1888 was one of the earliest and most famous successful worker strikes and perhaps the beginning of ``militant trade unionism''~\cite{10.2307/3827491}.
% As \citeauthor{weyer1894history} described, ``the match--girls' victory turned a new leaf in Trade Union annals''~\cite{weyer1894history}: in the 30 years after the match--girls strike, the Trade Union Movement enrollment grew from 20\% of eligible workers to over 60\%.
% This strike was followed by others, including women in the garment industry in Philadelphia who established collective bargaining rights~\cite{10.2307/41829256} and national coal miners who effected an individual minimum wage in 1912~\cite{10.2307/2221944}.
% The adoption of piecework's time--studies and other Taylorist and scientific management approaches reliably precipitated strikes and more generally gave workers a clear enemy against which to rally~\cite{jacoby1983union}.

@@

\subsubsection{\whatchanged}

\begin{comment}
	*workers make little money but love autonomy --- workers make little money
	workers blamed for quality --- ???
	both cases, sociality is hard
	*collective action hard --- collective action succeeded

	- algorithms, not managers
\end{comment}

@@

% \topic{The differences between crowd workers and pieceworkers seem defined largely by
% the differences in the places of work.}
% Whereas it arguably became inevitable that workers would have a place to
% meet, discuss, and collaborate
% when they began sharing places of work,
% online spaces make it much harder to do so.
% Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
% without any affiliation with
% --- or even knowledge of ---
% communities of peers
% % \ali{multiple citations that labor unions came out of factories here}
% \cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

@@

% \ali{here's an idea. feel free to push back or revise or something:\\
% ``Should we be surprised that
% management approaches we've known to
% frustrate pieceworkers since \citeyear{10.2307/2555446}
% would only aggravate crowd workers in many of the same ways?''}

@@

\subsubsection{\implication}

%	*workers make little money but love autonomy --- workers make little money
%	workers blamed for quality --- ???
%	both cases, sociality is hard
%	*collective action hard --- collective action succeeded
%	- algorithms, not managers

@@

\topic{The history of piecework further suggests that relationships between workers and employers might be improved if employers engaged in more human management styles.}
% \citeauthor{10.2307/2555446} drew a dichotomous line between
% ``defective (simple, observable) output measures'' and
% ``a manager's subjective judgment'',
% but such a dichotomy need not necessarily represent our work management styles
% \cite{10.2307/2555446}.
Instead of delegating as many management tasks as possible to an algorithm, it might be possible to build dashboards and other information tools that empower modern crowd work foremen~\cite{kulkarni2012mobileworks}.
If the literature on piecework is to be believed,
more considerate \textit{human} management may resolve
many of the tensions we've discovered among among crowd workers.

@@

% \paragraph[relationships to work]{Relationships to work}\label{ch:workRelationship}
% \topic{A number of ethical questions surrounding the
% increasing complexity of crowd work have arisen in recent years.}
% \citeauthor{professionalcrowdworkEthics} bring some of these issues to light
% --- working for increasing amounts of time on tasks of growing complexity%
% , only to discover that requesters are not willing to pay%
% , for instance ---
% but these and other dangers range an enormous landscape
% \cite{professionalcrowdworkEthics}.
% \citeauthor{crowdworkFuture}
% list a few of the problems they identified in \citeyear{crowdworkFuture}
% --- motivation, feedback, reputation, quality control, to name a few ---
% while others discuss challenges such as fostering collective action
% and the opportunity for learning and career advancement
% \cite{crowdworkFuture,nickerson2013crowd,dynamo}.

% Some research already looks at research such as investing in workers, and
% informally, we know that this happens among industry requesters
% \cite{jonBrelig,shepherdingDow}.
% AMT, meanwhile, offers requesters the ability to create tasks which are
% not just hidden from unqualified workers by default, but completely.
% Requesters have taken to using lists of worker IDs which reference
% workers who have proven their reliability,
% representing a sort of proto--organization of loosely connected workers.

% \subsubsubsection{\pieceworkpers}
% The rise of labor unions in the \nth{20} century seems to have been precipitated by
% egregiously unjust conditions imposed on workers in factories and elsewhere
% \cite{ebbinghaus1999institutions}.
% Incidents broadly describing this dynamic can be found in research on AMT
% \cite{turkopticon,dynamo}.
% If these are prototypical labor advocacy organizations of contemporary on--demand work,
% the next question we should look to is if
% --- and indeed \textit{how} ---
% these institutions might face challenges in the future.

% For insight on this, we return to \citeyear{levi2009union}'s study of labor unions,
% and identify that
% ``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
% \cite{levi2009union}.
% Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
% This perception already appears to be emerging in digitally mediated peer--governed organizations,
% as \citeauthor{keegan2010egalitarians} and others have illustratively documented
% \cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
% If these organizations and others are to avoid the same fate that labor unions faced,
% they should take care to study this phenomenon and attempt to avoid it.

% \subsubsubsection{\whatchanged}
% \topic{While online and distributed workers can be harder to find,
% other features make the study thereof rewarding for the substantively different ways
% that we can approach their study.}
% The longitudinal analysis of everyday discourse, for instance,
% is trivial in the study of online communities

% \subsubsubsection{\implication}

% \onlyinsubfile{
% \balance{}
% \printbibliography
% }
\end{document}

>>>>

\onlyinsubfile{\newpage}
\subsubsection{\crowdworkpers}
\begin{comment}
	- Workers do it for money
	- Workers coordinate and communicate (gray, being a turker, team stuff). there is mega-drama
	- Workers don't like requesters. have tried to organize
\end{comment}

@@

Workers' relationships with requesters are fraught.
Workers are often blamed for any low-quality work, regardless of whether they are responsible~\cite{martin2014being,takingAHITMcInnis}.
Some research is extremely open about this position, blaming unpredictable work on ``malicious'' workers~\cite{MaliciousCrowdworkersGadiraju} or those with ``a lack of expertise, dedication [or] interest''~\cite{Sheng:2008:GLI:1401890.1401965}.
Workers resent this position --- for good reason.
\citeauthor{turkopticon} highlighted the information asymmetry between workers and requesters on AMT, leading to the creation of \TO, a site which allows Turkers to rate and review requesters~\cite{turkopticon}.
Dynamo then took this critique on information asymmetry and power imbalances a step further, designing a platform to facilitate
Turkers acting collectively to bring about changes to their circumstances~\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters~\cite{fixingChaos,dynamo}.

@@

\onlyinsubfile{\newpage}
\subsubsection{\pieceworkpers}
Early observers believed that workers were strongly motivated by the piecework model.
\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand.''
Workers' situations were quite dire: \citeauthor{riisOtherSideLives}  documented abhorrent working and living conditions of pieceworkers in New York City~\cite{riisOtherSideLives}.

@@

\onlyinsubfile{\newpage}
\subsubsection{\whatchanged}

\begin{comment}
	*workers make little money but love autonomy --- workers make little money
	workers blamed for quality --- ???
	both cases, sociality is hard
	*collective action hard --- collective action succeeded
	- algorithms, not managers
\end{comment}

@@

@@

@@

\onlyinsubfile{\newpage}
\subsubsection{\implication}

@@

\topic{The history of piecework further suggests that relationships between workers and employers might be improved if employers engaged in more human management styles.}
Instead of delegating as many management tasks as possible to an algorithm, it might be possible to build dashboards and other information tools that empower modern crowd work foremen~\cite{kulkarni2012mobileworks}.
If the literature on piecework is to be believed,
more considerate \textit{human} management may resolve
many of the tensions we've discovered among among crowd workers.

@@

\onlyinsubfile{
\balance{}
\printbibliography
}
\end{document}
